---
title: "R and Reproducibility"
author: "Andre Fonseca"
date: "November 17, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}

# https://ulyngs.github.io/rmarkdown-workshop-2019/slides/Day2.html#83
# https://stanford.edu/~vbauer/teaching/rmarkdown.html
# http://www.geo.uzh.ch/microsite/reproducible_research/post/rr-rstudio-git/

# Rstudio
# Utilities
# Project management
# Rmarkdown and Rnotebooks
# Git...
# Print screens
# Extra: Bookdown and Blogdown
# Extra: Shiny Apps



```

## Slide with Plot

```{r pressure}
plot(pressure)
```

