---
title: "R and Reproducibility"
author: "Andre Fonseca"
date: "November 17, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}

# https://ulyngs.github.io/rmarkdown-workshop-2019/slides/Day2.html#83
# https://stanford.edu/~vbauer/teaching/rmarkdown.html
# http://www.geo.uzh.ch/microsite/reproducible_research/post/rr-rstudio-git/
# https://datacarpentry.org/rr-intro/02-toolkit/

# Rstudio
## A looking throught the panes
# Utilities
## Shortcuts
## Add-ons

# An work about reproducibility and project management
## A real world scenario
## Starting a project using RStudio

# https://www.tidyverse.org/blog/2017/12/workflow-vs-script/

# Communicate your results using R
## Rmarkdown and Rnotebooks
## Markdonw syntax: Document style
## Import external elements
### Images and animations
## Saving as HTML, pdf or doc
## Re-scale figures

# https://daringfireball.net/projects/markdown/dingus
# https://daijiang.name/en/2017/04/05/writing-academic-papers-with-rmarkdown/ 

# Git and code version
## What is git?
## Basic commands: init, add, commit, push, pull and status
## Fundamental workflow
## .gitignore

# https://education.github.com/git-cheat-sheet-education.pdf
# https://github.github.com/training-kit/downloads/github-git-cheat-sheet.pdf
# https://dev.to/sublimegeek/git-staging-area-explained-like-im-five-1anh
# https://dzone.com/articles/top-20-git-commands-with-examples
# https://rogerdudler.github.io/git-guide/

# Extra: Bookdown and Blogdown
# Extra: Shiny Apps

## 


```

## Slide with Plot

```{r pressure}
plot(pressure)
```

